Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-12-22 manuscript.Rmd
Update corpus stats

author:
  - name          : "Megan Chiovaro"
    affiliation   : "1, 2"
    corresponding : yes    # Define only one corresponding author
    address       : "406 Babbidge Road, Unit 1020, Storrs, CT 06269"
    email         : "megan.chiovaro@uconn.edu"
  - name          : "Alexandra Paxton"
    affiliation   : "1,2,*"
  - name          : "Leah C. Windsor"
    affiliation   : "3,*"

affiliation:
  - id            : "1"
    institution   : "Center for the Ecological Study of Perception and Action, University of Connecticut"
  - id            : "2"
    institution   : "Department of Psychological Sciences, University of Connecticut"
  - id            : "3"
    institution   : "University of Memphis"
  - id            : "*"
    institution   : "Equal author contributions"

@@

```{r num-tweets, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE}

#num_tweets <- read.csv("./data/raw/Syria-social_cohesion.csv")

@@

The corpus of tweets used included r sum(num_tweets$n) (ADD TICKS) Syrian tweets
occurring between March 30--June 15, 2012. Using the Twitter streaming API,
servers at the University of Texas at Austin collected the tweets. The servers
were run on a stable (LTS) version of Ubuntu Linus (v. 10.04) and were connected
directly to the high-bandwidth UT network maintained by IT services.

@@

All scripts used for scraping tweets and compressing data can be found at
https://github.com/chbrown/twilight.

### Event Data
Event data were obtained from the 2012 Integrated Crisis Early Warning System
[ICEWS; @DVN/28075_2015]. The event data were first filtered to remove
incomplete and incorrectly formatted data. They were then filtered to include
only events that were directed at (i.e., `target`) Syria ($n = 6300$). To
explore the impact of outwardly directed Syrian events, the data were filtered
again to include events that were both directed at (i.e., `target`) or directed
by (i.e., `source`) Syria ($n = 7990$).

>>>>

author:
  - name          : "Megan Chiovaro"
    affiliation   : "1, 2"
    corresponding : yes    # Define only one corresponding author
    address       : "406 Babbidge Road, Unit 1020, Storrs, CT 06269"
    email         : "megan.chiovaro@uconn.edu"
  - name          : "Leah C. Windsor"
    affiliation   : "3,*"
  - name          : "Alistair Windsor"
    affiliation   : "4"
  - name          : "Alexandra Paxton"
    affiliation   : "1,2,*"

affiliation:
  - id            : "1"
    institution   : "Center for the Ecological Study of Perception and Action, University of Connecticut"
  - id            : "2"
    institution   : "Department of Psychological Sciences, University of Connecticut"
  - id            : "3"
    institution   : "Institute for Intelligent Systems, University of Memphis"
  - id            : "4"
    institution   : "Department of Mathematical Sciences, University of Memphis"
  - id            : "*"
    institution   : "Equal author contributions"

@@

```{r corpus_stats, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE}

tweet_stats <- read.csv("./data/formatted/primary/stats.csv")

@@

The corpus of tweets used included `r tweet_stats$total_tweets` Syrian tweets
occurring between March 30--June 15, 2012. Using the Twitter streaming API,
servers at the University of Texas at Austin collected the tweets. The servers
were run on a stable (LTS) version of Ubuntu Linus (v. 10.04) and were connected
directly to the high-bandwidth UT network maintained by IT services.

@@

The corpus consisted of `r tweet_stats$percent_original_tweets`% original tweets and `r tweet_stats$percent_retweets_all`% retweets. There were `r tweet_stats$num_users` users in the corpus, and an average of `r tweet_stats$avg_daily_tweets` tweets per day.

Scripts used for scraping tweets and compressing data can be found at
https://github.com/chbrown/twilight.

### Event Data
Event data were obtained from the 2012 Integrated Crisis Early Warning System
[ICEWS; @DVN/28075_2015]. The event data were first filtered to remove
incomplete and incorrectly formatted data. They were then filtered to include
only events that were directed at (i.e., `target`) Syria ($n = INSERT NUMBER HERE$). To
explore the impact of outwardly directed Syrian events, the data were filtered
again to include events that were both directed at (i.e., `target`) or directed
by (i.e., `source`) Syria ($n = INSERT NUMBER HERE$).
